Hybrid compiler-library approach to efficiently compile Numpy expressions

### 2013-04-05 doc/papers/cpc2013/paper.tex

\author{Serge Guelton\inst{1} \and Joël Falcou\inst{2} \and Pierrick Brunet\inst{3}}
\institute{ENS ULM, Paris, France \and LRI, University Paris Sud XI, France \and Télécom Bretagne, Plouzané, France}

>>>>

\author{Serge Guelton\inst{1} \and Pierrick Brunet\inst{2} \and Pierre Esterie\inst{3}\\
 \and Mathias Gaunard\inst{4} \and Joël Falcou\inst{3} }
\institute{ENS ULM, Paris, France \and Télécom Bretagne, Plouzané, France \and LRI, University Paris Sud XI, France  \and MetaScale SAS, Orsay, France}
